---
title: "MLB Dashboard"
output: 
  flexdashboard::flex_dashboard:
    css: my-custom-rules.css
    theme:
      bg: "white"
      fg: "black" 
      base_font:
        google: "Exo 2"
    orientation: rows
---

<style>


body {
  padding-top:0px;
  background-color: white;
  font-family: Exo 2;
}




pre {
        border: 0;
    }

.navbar{
  visibility: hidden;
  background-color:white;
  border-color:white;
}

.navbar-brand {
color:black!important;
}

.doc_main {
    margin-left: 260px;
    font-size: 12px;
    font-family: Exo 2;
    line-height: 2;
  }


</style>




```{r setup, include=FALSE}
library(flexdashboard) 
library(tidyverse)
library(gtExtras)
library(gt)
library(cowplot)
library(showtext)
font_add_google("Exo 2")

# Install thematic and un-comment for themed static plots (i.e., ggplot2)
library(thematic)
 thematic::thematic_rmd()
 
#load packages
library("baseballr")
library(readr)

player_batting <- read.csv("player_batting.csv")
player_batting_splits <- read.csv("player_batting_splits.csv")
team_batting <- read.csv("team_batting.csv")
team_batting_splits <- read.csv("team_batting_splits.csv")
team_pitching <- read.csv("team_pitching.csv")
team_pitching_splits <- read.csv("team_pitching_splits.csv")
player_starting_pitching <- read.csv("player_starting_pitching.csv")
player_relief_pitching <- read.csv("player_relief_pitching.csv")
player_pitching_splits <- read.csv("player_pitching_splits.csv")

#round IP
player_starting_pitching$ip <- round(player_starting_pitching$ip,0)
player_relief_pitching$ip <- round(player_relief_pitching$ip,0)
player_pitching_splits$ip <- round(player_pitching_splits$ip,0)



#remove trailing 0
#batting
player_batting$avg <- ifelse(player_batting$avg < .1, paste0('.0', player_batting$avg*1000), paste0('.', player_batting$avg*1000))
player_batting$slg <- ifelse(player_batting$slg < .1, paste0('.0', player_batting$slg*1000), paste0('.', player_batting$slg*1000))
player_batting$obp <- ifelse(player_batting$obp < .1, paste0('.0', player_batting$obp*1000), paste0('.', player_batting$obp*1000))
player_batting$iso <- ifelse(player_batting$iso < .1, paste0('.0', player_batting$iso*1000), paste0('.', player_batting$iso*1000))
player_batting$xba <- ifelse(player_batting$xba < .1, paste0('.0', player_batting$xba*1000), paste0('.', player_batting$xba*1000))
player_batting$xslg <- ifelse(player_batting$xslg < .1, paste0('.0', player_batting$xslg*1000), paste0('.', player_batting$xslg*1000))
player_batting$xwoba <- ifelse(player_batting$xwoba < .1, paste0('.0', player_batting$xwoba*1000), paste0('.', player_batting$xwoba*1000))

#player batting splits
player_batting_splits$avg <- ifelse(player_batting_splits$avg < .1, paste0('.0', player_batting_splits$avg*1000), paste0('.', player_batting_splits$avg*1000))
player_batting_splits$slg <- ifelse(player_batting_splits$slg < .1, paste0('.0', player_batting_splits$slg*1000), paste0('.', player_batting_splits$slg*1000))
player_batting_splits$obp <- ifelse(player_batting_splits$obp < .1, paste0('.0', player_batting_splits$obp*1000), paste0('.', player_batting_splits$obp*1000))
player_batting_splits$iso <- ifelse(player_batting_splits$iso < .1, paste0('.0', player_batting_splits$iso*1000), paste0('.', player_batting_splits$iso*1000))

#player starting pitching
player_starting_pitching$avg <- ifelse(player_starting_pitching$avg < .1, paste0('.0', player_starting_pitching$avg*1000), paste0('.', player_starting_pitching$avg*1000))
player_starting_pitching$babip <- ifelse(player_starting_pitching$babip < .1, paste0('.0', player_starting_pitching$babip*1000), paste0('.', player_starting_pitching$babip*1000))

#player relief pitching
player_relief_pitching$avg <- ifelse(player_relief_pitching$avg < .1, paste0('.0', player_relief_pitching$avg*1000), paste0('.', player_relief_pitching$avg*1000))
player_relief_pitching$babip <- ifelse(player_relief_pitching$babip < .1, paste0('.0', player_relief_pitching$babip*1000), paste0('.', player_relief_pitching$babip*1000))

#player pitching splits
player_pitching_splits$avg <- ifelse(player_pitching_splits$avg < .1, paste0('.0', player_pitching_splits$avg*1000), paste0('.', player_pitching_splits$avg*1000))
player_pitching_splits$obp <- ifelse(player_pitching_splits$obp < .1, paste0('.0', player_pitching_splits$obp*1000), paste0('.', player_pitching_splits$obp*1000))
player_pitching_splits$slg <- ifelse(player_pitching_splits$slg < .1, paste0('.0', player_pitching_splits$slg*1000), paste0('.', player_pitching_splits$slg*1000))
player_pitching_splits$woba <- ifelse(player_pitching_splits$woba < .1, paste0('.0', player_pitching_splits$woba*1000), paste0('.', player_pitching_splits$woba*1000))

#team batting
team_batting$avg <- ifelse(team_batting$avg < .1, paste0('.0', team_batting$avg*1000), paste0('.', team_batting$avg*1000))
team_batting$slg <- ifelse(team_batting$slg < .1, paste0('.0', team_batting$slg*1000), paste0('.', team_batting$slg*1000))
team_batting$obp <- ifelse(team_batting$obp < .1, paste0('.0', team_batting$obp*1000), paste0('.', team_batting$obp*1000))
team_batting$iso <- ifelse(team_batting$iso < .1, paste0('.0', team_batting$iso*1000), paste0('.', team_batting$iso*1000))

#team batting splits
team_batting_splits$avg <- ifelse(team_batting_splits$avg < .1, paste0('.0', team_batting_splits$avg*1000), paste0('.', team_batting_splits$avg*1000))
team_batting_splits$slg <- ifelse(team_batting_splits$slg < .1, paste0('.0', team_batting_splits$slg*1000), paste0('.', team_batting_splits$slg*1000))
team_batting_splits$obp <- ifelse(team_batting_splits$obp < .1, paste0('.0', team_batting_splits$obp*1000), paste0('.', team_batting_splits$obp*1000))
team_batting_splits$iso <- ifelse(team_batting_splits$iso < .1, paste0('.0', team_batting_splits$iso*1000), paste0('.', team_batting_splits$iso*1000))

#team pitching
team_pitching$avg <- ifelse(team_pitching$avg < .1, paste0('.0', team_pitching$avg*1000), paste0('.', team_pitching$avg*1000))
team_pitching$babip <- ifelse(team_pitching$babip < .1, paste0('.0', team_pitching$babip*1000), paste0('.', team_pitching$babip*1000))

#team pitching splits
team_pitching_splits$avg <- ifelse(team_pitching_splits$avg < .1, paste0('.0', team_pitching_splits$avg*1000), paste0('.', team_pitching_splits$avg*1000))
team_pitching_splits$obp <- ifelse(team_pitching_splits$obp < .1, paste0('.0', team_pitching_splits$obp*1000), paste0('.', team_pitching_splits$obp*1000))
team_pitching_splits$slg <- ifelse(team_pitching_splits$slg < .1, paste0('.0', team_pitching_splits$slg*1000), paste0('.', team_pitching_splits$slg*1000))
team_pitching_splits$woba <- ifelse(team_pitching_splits$woba < .1, paste0('.0', team_pitching_splits$woba*1000), paste0('.', team_pitching_splits$woba*1000))


mlb_standings <- read.csv("standings.csv")
#convert date field to date
mlb_standings$date <- as.Date(mlb_standings$date, format = "%Y-%m-%d") 
#nudge images to the right for certain teams
mlb_standings$nudge_runs_plot <- ifelse(mlb_standings$team_abbr %in% c("PIT", "SF", "NYM", "SD", "LAD"), .01, 0)
mlb_standings$nudge_div_race_plot <- ifelse(mlb_standings$team_abbr %in% c("PIT", "SF", "NYM", "SD", "AD"), .017, 0)
#adjust image size so all logos are nearly the same size when in plots
mlb_standings$runs_plot_image_size_adj <- ifelse(mlb_standings$team_abbr %in% c("CHC", "BAL", "HOU", "TOR", "OAK", "CIN"), 0.013, 0)
mlb_standings$div_race_image_size_adj <- ifelse(mlb_standings$team_abbr %in% c("CHC", "BAL", "HOU", "TOR", "OAK", "CIN"), 0.007, 0)

#set fill color to be used for certain teams
mlb_standings$gg_fill_color <- ifelse(mlb_standings$team_abbr %in% c("TOR", "NYM", "MIA", "MIL", "PIT"), mlb_standings$team_color, ifelse(mlb_standings$team_abbr %in% c("MIN"), "#B9975B", ifelse(mlb_standings$team_abbr %in% c("TEX"), "#D1E5F4", mlb_standings$team_color2)))

#set border/line color to be used for plots for certain teams
mlb_standings$gg_color <- ifelse(mlb_standings$team_abbr %in% c("TOR", "NYM", "MIL", "PIT"), mlb_standings$team_color2, ifelse(mlb_standings$team_abbr %in% c("MIA"), "black", mlb_standings$team_color))

#update mlb_standings team abbreviations to match fangraphs data
mlb_standings$team_abbr <- case_when(
    mlb_standings$team_abbr == "TB" ~ "TBR",
    mlb_standings$team_abbr == "AZ" ~ "ARI",
    mlb_standings$team_abbr == "CWS" ~ "CHW",
    mlb_standings$team_abbr == "KC" ~ "KCR",
    mlb_standings$team_abbr == "SD" ~ "SDP",
    mlb_standings$team_abbr == "SF" ~ "SFG",
    mlb_standings$team_abbr == "WSH" ~ "WSN",
    TRUE ~ mlb_standings$team_abbr
)

#filter to most recent date for overall season plots and for final points/logos on div trend plot
mlb_standings_max <- mlb_standings %>% filter(date == max(date))

#write.csv(mlb_team_logos, "mlb_team_logos.csv", row.names = FALSE)

#mlb_team_logos <- read.csv("mlb_team_logos.csv")

#create theme for runs plot
runs_plot_theme <- function() { 
  theme_minimal(base_size = 9, base_family = "Exo 2") %+replace%
    theme(axis.text = element_text(size=7), 
          axis.text.x=element_text(vjust=0),
          axis.text.y=element_text(hjust=0),
          axis.title= element_text(size=8), 
          axis.title.x= element_text(vjust = -2),
          axis.title.y= element_text(angle = 90, vjust = 3.5),
          plot.title=element_text(size = 10, 
                                  face="bold", 
                                  color = team_color,  
                                  margin = margin(b = 10), 
                                  hjust = 0.5),
          plot.subtitle=element_text(size = 10, 
                                     vjust = 2.5),
          panel.grid.minor = element_blank(),
          panel.grid.major = element_line(color = alpha("grey", .1)),
          plot.margin=margin(b=1, t = .5, l=5.5,r=3, unit="lines")
          ) }

library("ggimage")

#make images transparent
library(magick)
transparent <- function(img) {
  magick::image_fx(img, expression = ".7*a", channel = "alpha")
}


#create player batting table theme
player_batting_table_theme <- function(data, ...) {
  data  %>%
    # Relabel columns
    cols_label(
      name = "",
      #pa_rk = "pa",
      avg_rk = "avg",
      obp_rk = "obp",
      slg_rk = "slg",
      iso_rk = "iso",
      bbk_rk = "bb/k",
      o_swing_rk = "chase%",
      csw_rk = "csw%",
      contact_rk = "contact%",
      soft_rk = "soft%",
      med_rk = "med%",
      hard_rk = "hard%",
      barrel_rk = "barrel%",
      pull_rk = "pull%",
      cent_rk = "center%",
      oppo_rk = "oppo%",
      wrc_rk = "wrc+",
      war_rk = "war",
      xba_rk = "xba",
      xslg_rk = "xslg",
      xwoba_rk = "xwoba"
    ) %>%
    # Make column labels and spanners all caps
    opt_all_caps() %>%
    # add row striping
    opt_row_striping() %>%
    # change overall table styling for borders and striping
    tab_options(
      column_labels.background.color = "#363231",
      table_body.hlines.color = alpha("gray99", alpha = 0),
      table.border.top.style = "hidden",
      table.border.bottom.style = "hidden",
      table.border.top.width = px(3),
      table.border.top.color = alpha("gray99", alpha = 0),
      table.border.bottom.color = alpha("gray99", alpha = 0),
      table.border.bottom.width = px(3),
      column_labels.border.top.width = px(3),
      column_labels.border.top.color = alpha("gray99", alpha = 0),
      column_labels.border.bottom.width = px(3),
      column_labels.border.bottom.color = alpha("#BEC2CB", alpha = 1),
      heading.title.font.size = 10,
      heading.align = "left",
      # remove padding so player splits fit on one page
      source_notes.padding = px(0),
      
      #row.striping.background_color = "#f9f9fb",
      column_labels.font.size = 8,
      column_labels.font.weight = "bold",
      table.margin.left = px(50),
      ...
    ) %>%
    cols_width(
      1 ~ px(118),
      pa ~ px(35.5),
      #Contact %
      everything() ~ px(47.84)
    ) %>% 
    # change color of border separating the text from the sourcenote
    tab_style(
      style = cell_borders(
        sides = "bottom", color = "#585d63", weight = px(2)
      ),
      locations = cells_body(
        columns = everything(),
        rows = nrow(data$`_data`)
      )
    ) %>%
    #center align values
    tab_style(
    style = cell_text(align = "center"),
    locations = cells_body(
      columns = everything())) %>%
    #center align col headers
    tab_style(
      style = cell_text(align = "center"),
      locations = cells_column_labels(
        columns = everything())) %>%
    #prevent player name from wrapping
    tab_style(
      style = cell_text(whitespace = "nowrap", size = px(12), color = "black", align = "left"),
      locations = cells_body(
        columns = name,
    )) %>%
    #pa font adjustment
    tab_style(
      style = cell_text(size = px(12), color = "black", align = "center"),
      locations = cells_body(
        columns = pa,
      )) %>%
    # change font to Lato throughout (note no need to have Lato locally!)
    opt_table_font(
      font = c(
        google_font(name = "Exo 2"),
        default_fonts()
      )
    ) %>%
     #change table heading color
      tab_style(
    style = list(
      cell_text(
        align = "left",
        weight = 'bold',
        color = team_color
      )
    ),
    locations = list(
      cells_title(groups = c("title"))
    )
  ) %>%
    # add source note
    tab_source_note(
      source_note = md("")
    )
}


team_batting_table_theme <- function(data, ...) {
  data  %>%
    # Relabel columns
    cols_label(
      team = "",
      avg_rk = "avg",
      obp_rk = "obp",
      slg_rk = "slg",
      iso_rk = "iso",
      bb_rk = "bb%",
      k_rk = "k%",
      bbk_rk = "bb/k",
      o_swing_rk = "chase%",
      csw_rk = "csw%",
      contact_rk = "contact%",
      soft_rk = "soft%",
      med_rk = "med%",
      hard_rk = "hard%",
      barrel_rk = "barrel%",
      pull_rk = "pull%",
      cent_rk = "center%",
      oppo_rk = "oppo%",
      wrc_rk = "wrc+"
    ) %>%
    # Make column labels and spanners all caps
    opt_all_caps() %>%
    # add row striping
    opt_row_striping() %>%
    # change overall table styling for borders and striping
    tab_options(
      column_labels.background.color = "#363231",
      table_body.hlines.color = alpha("gray99", alpha = 0),
      table.border.top.style = "hidden",
      table.border.bottom.style = "hidden",
      table.border.top.width = px(3),
      table.border.top.color = alpha("gray99", alpha = 0),
      table.border.bottom.color = alpha("gray99", alpha = 0),
      table.border.bottom.width = px(3),
      column_labels.border.top.width = px(3),
      column_labels.border.top.color = alpha("gray99", alpha = 0),
      column_labels.border.bottom.width = px(3),
      column_labels.border.bottom.color = alpha("#BEC2CB", alpha = 1),
      heading.title.font.size = 10,
      heading.align = "left",
      
      #row.striping.background_color = "#f9f9fb",
      column_labels.font.size = 8,
      column_labels.font.weight = "bold",
      table.margin.left = px(50),
      ...
    ) %>%
    cols_width(
      team ~ px(42),
      everything() ~ px(59.35)
    ) %>% 
    # change color of border separating the text from the sourcenote
    tab_style(
      style = cell_borders(
        sides = "bottom", color = "#585d63", weight = px(2)
      ),
      locations = cells_body(
        columns = everything(),
        rows = nrow(data$`_data`)
      )
    ) %>%
    #center align values
    tab_style(
    style = cell_text(align = "center"),
    locations = cells_body(
      columns = everything())) %>%
    #center align col headers
    tab_style(
      style = cell_text(align = "center"),
      locations = cells_column_labels(
        columns = everything())) %>%
    #prevent team name from wrapping
    tab_style(
      style = cell_text(whitespace = "nowrap", size = px(12), color = "black", align = "left"),
      locations = cells_body(
        columns = team,
    )) %>%
    # change font to Lato throughout (note no need to have Lato locally!)
    opt_table_font(
      font = c(
        google_font(name = "Exo 2"),
        default_fonts()
      )
    ) %>%
     #change table heading color
      tab_style(
    style = list(
      cell_text(
        align = "left",
        weight = 'bold',
        color = team_color
      )
    ),
    locations = list(
      cells_title(groups = c("title"))
    )
  ) %>%
    # add source note
    tab_source_note(
      source_note = md("")
    )
}

#custom theme to make label blank for bar in table
gt_plt_bar_custom <- function(gt_object,
                       column = NULL,
                       color = "purple",
                       ...,
                       keep_column = FALSE,
                       width = 70,
                       scale_type = "none",
                       text_color = "white") {
  stopifnot(
    "'gt_object' must be a 'gt_tbl',
            have you accidentally passed raw data?" = "gt_tbl" %in% class(gt_object)
  )
  stopifnot(
    "`scale_type` must be one of 'number', 'percent' or 'none'" =
      scale_type %in% c("number", "percent", "none")
  )

  var_sym <- rlang::enquo(column)
  var_bare <- rlang::as_label(var_sym)
  col_bare <- var_bare

  all_vals <- gt_index(gt_object, {{ column }}) %>%
    unlist()

  # need to handle truly empty cols
  if (length(na.omit(all_vals)) == 0) {
    return(gt_object)
  }

  stopifnot(
    "Colors must be either length 1 or equal length to the column" =
      isTRUE(length(color) == 1 | length(color) == length(all_vals))
  )

  stopifnot("'text_color' must be length 1" = length(text_color) == 1)

  if (length(color) == 1) {
    colors <- rep(color, length(all_vals))
  } else if (length(color) == length(all_vals)) {
    colors <- color
  }

  if ((min(all_vals, na.rm = TRUE) >= 0)) {
    min_val <- 0
    rng_multiplier <- c(0.98, 1.02)
  } else if (
    (max(all_vals, na.rm = TRUE) < 0 & min(all_vals, na.rm = TRUE) < 0)
    ) {
    min_val <- min(all_vals, na.rm = TRUE)
    rng_multiplier <- c(1.02, 0)
  } else {
    min_val <- min(all_vals, na.rm = TRUE)
    rng_multiplier <- c(1.02, 1.02)
  }

  total_rng <- c(min_val, max(all_vals, na.rm = TRUE)) * rng_multiplier

  if (isTRUE(keep_column)) {
    gt_object <- gt_object %>%
      gt_duplicate_column({{ column }}, dupe_name = "DUPE_COLUMN_PLT")
  }

  bar_fx <- function(x_val, colors) {
    if (x_val %in% c("NA", "NULL", NA)) {
      return("<div></div>")
    }


    vals <- as.double(x_val)

    df_in <- dplyr::tibble(
      x = vals,
      y = rep(1),
      fill = colors
    )

    plot_out <- df_in %>%
      ggplot(
        aes(
          x = .data$x,
          y = factor(.data$y),
          fill = I(.data$fill),
          group = .data$y
        )
      ) +
      geom_col(color = "transparent", width = 0.3) +
      scale_x_continuous(
        limits = total_rng,
        expand = expansion(mult = c(0.05, 0.08)),
      ) +
      scale_y_discrete(expand = expansion(mult = c(0.2, 0.2))) +
      geom_vline(xintercept = 0, color = "black", linewidth = 1) +
      coord_cartesian(clip = "off") +
      theme_void() +
      theme(legend.position = "none", plot.margin = unit(rep(0, 4), "pt"))

    if (scale_type != "none") {
      plot_out <- plot_out +
        geom_text(
          aes(
            x = .data$x,
            label = if (scale_type == "number") {
              scales::label_number(...)(.data$x)
            } else if (scale_type == "percent") {
              scales::label_percent(...)(.data$x)
            },
            hjust = ifelse(.data$x >= 0, 1, 0)
          ),
          nudge_x = sign(df_in$x) * (-1) / 80,
          vjust = 0.5,
          size = 3,
          family = "mono",
          color = text_color,
          fontface = "bold"
        )
    }

    out_name <- file.path(tempfile(
      pattern = "file",
      tmpdir = tempdir(),
      fileext = ".svg"
    ))

    ggsave(
      out_name,
      plot = plot_out,
      dpi = 25.4,
      height = 5,
      width = width,
      units = "mm",
      device = "svg"
    )

    img_plot <- readLines(out_name) %>%
      paste0(collapse = "") %>%
      gt::html()

    on.exit(file.remove(out_name), add = TRUE)

    img_plot
  }


  tab_out <- text_transform(
    gt_object,
    locations = if (isTRUE(keep_column)) {
      cells_body(columns = c("DUPE_COLUMN_PLT"))
    } else {
      cells_body(columns = {{ column }})
    },
    fn = function(x) {
      tab_built <- mapply(bar_fx, x_val = x, colors = colors)
    }
  )

  if (isTRUE(keep_column)) {
    tab_out %>%
      cols_label(DUPE_COLUMN_PLT = " ") %>%
      cols_align("left", columns = c(DUPE_COLUMN_PLT))
  } else {
    tab_out %>%
      cols_label(bar = " ") %>%
      cols_align("left", columns = {{ column }})
  }
}

team_batting_splits_table_theme <- function(data, ...) {
  data  |>
    # Relabel columns
    cols_label(
      team = "",
      avg_rk = "avg",
      obp_rk = "obp",
      slg_rk = "slg",
      iso_rk = "iso",
      bbk_rk = "bb/k",
      wrc_rk = "wrc+",
    ) |>
    # Make column labels and spanners all caps
    opt_all_caps() |>
    # add row striping
    opt_row_striping() |>
    # change overall table styling for borders and striping
    tab_options(
      column_labels.background.color = "#363231",
      table_body.hlines.color = alpha("gray99", alpha = 0),
      table.border.top.style = "hidden",
      table.border.bottom.style = "hidden",
      table.border.top.width = px(3),
      table.border.top.color = alpha("gray99", alpha = 0),
      table.border.bottom.color = alpha("gray99", alpha = 0),
      table.border.bottom.width = px(3),
      column_labels.border.top.width = px(3),
      column_labels.border.top.color = alpha("gray99", alpha = 0),
      column_labels.border.bottom.width = px(3),
      column_labels.border.bottom.color = alpha("#BEC2CB", alpha = 1),
      heading.title.font.size = 10,
      heading.align = "left",
      
      #row.striping.background_color = "#f9f9fb",
      column_labels.font.size = 8,
      column_labels.font.weight = "bold",
      table.margin.left = px(50),
      ...
    ) |>
    cols_width(
      1 ~ px(42),
      2 ~ px(54.5),
      3 ~ px(54.5),
      4 ~ px(54.5),
      5 ~ px(54.5),
      6 ~ px(54.5),
      7 ~ px(54.5),
      8 ~ px(54.5),
      9 ~ px(54.5),
      10 ~ px(54.5),
      11 ~ px(54.5),
      12 ~ px(54.5),
      13 ~ px(54.5),
      14 ~ px(54.5)
    ) |> 
    # change color of border separating the text from the sourcenote
    tab_style(
      style = cell_borders(
        sides = "bottom", color = "#585d63", weight = px(2)
      ),
      locations = cells_body(
        columns = everything(),
        rows = nrow(data$`_data`)
      )
    ) |>
    #center align values
    tab_style(
      style = cell_text(align = "center"),
      locations = cells_body(
        columns = everything())) |>
    #center align col headers
    tab_style(
      style = cell_text(align = "center"),
      locations = cells_column_labels(
        columns = everything())) |>
    #prevent team name from wrapping
    tab_style(
      style = cell_text(whitespace = "nowrap", size = px(12), color = "black", align = "left"),
      locations = cells_body(
        columns = team,
      )) |>
    #split type font adjustment
    tab_style(
      style = cell_text(size = px(12), color = "black", align = "center"),
      locations = cells_body(
        columns = split,
      )) |>
    # change font to Lato throughout (note no need to have Lato locally!)
    opt_table_font(
      font = c(
        google_font(name = "Exo 2"),
        default_fonts()
      )
    ) |>
    #change table heading color
    tab_style(
      style = list(
        cell_text(
          align = "left",
          weight = 'bold',
          color = team_color
        )
      ),
      locations = list(
        cells_title(groups = c("title"))
      )
    ) |>
    # add source note
    tab_source_note(
      source_note = md("")
    )
}


player_batting_splits_table_theme <- function(data, ...) {
  data  |>
    # Relabel columns
    cols_label(
      name = "",
      avg_rk = "avg",
      obp_rk = "obp",
      slg_rk = "slg",
      iso_rk = "iso",
      bbk_rk = "bb/k",
      wrc_rk = "wrc+",
    ) |>
    # Make column labels and spanners all caps
    opt_all_caps() |>
    # add row striping
    opt_row_striping() |>
    # change overall table styling for borders and striping
    tab_options(
      column_labels.background.color = "#363231",
      table_body.hlines.color = alpha("gray99", alpha = 0),
      table.border.top.style = "hidden",
      table.border.bottom.style = "hidden",
      table.border.top.width = px(3),
      table.border.top.color = alpha("gray99", alpha = 0),
      table.border.bottom.color = alpha("gray99", alpha = 0),
      table.border.bottom.width = px(3),
      column_labels.border.top.width = px(3),
      column_labels.border.top.color = alpha("gray99", alpha = 0),
      column_labels.border.bottom.width = px(3),
      column_labels.border.bottom.color = alpha("#BEC2CB", alpha = 1),
      heading.title.font.size = 10,
      heading.align = "left",
      row_group.font.size = 9,
      row_group.padding = px(1),
      row_group.border.top.color = alpha("gray99", alpha = 0),
      row_group.border.bottom.width = px(.2),
      row_group.border.bottom.color = alpha("#BEC2CB", alpha = .3),
      #row.striping.background_color = "#f9f9fb",
      column_labels.font.size = 8,
      column_labels.font.weight = "bold",
      table.margin.left = px(50),
      ...
    ) |>
    cols_width(
      1 ~ px(42),
      2 ~ px(53),
      3 ~ px(53),
      4 ~ px(53),
      5 ~ px(53),
      6 ~ px(53),
      7 ~ px(53),
      8 ~ px(53),
      9 ~ px(53),
      10 ~ px(53),
      11 ~ px(53),
      12 ~ px(53),
      13 ~ px(53),
      14 ~ px(53),
      15 ~ px(53),
      16 ~ px(80)
    ) |> 
    #center align values
    tab_style(
      style = cell_text(align = "center"),
      locations = cells_body(
        columns = everything())) |>
    #center align col headers
    tab_style(
      style = cell_text(align = "center"),
      locations = cells_column_labels(
        columns = everything())) |>
    #prevent player name from wrapping
    tab_style(
      style = cell_text(whitespace = "nowrap", size = px(9), color = "black", align = "left"),
      locations = cells_body(
        columns = name,
    )) %>%
    #pa font adjustment
    tab_style(
      style = cell_text(size = px(12), color = "black", align = "center"),
      locations = cells_body(
        columns = pa,
      )) %>%
    #split type font adjustment
    tab_style(
      style = cell_text(size = px(12), color = "black", align = "center"),
      locations = cells_body(
        columns = split,
      )) |>
    # change font to Lato throughout (note no need to have Lato locally!)
    opt_table_font(
      font = c(
        google_font(name = "Exo 2"),
        default_fonts()
      )
    ) |>
    #change table heading color
    tab_style(
      style = list(
        cell_text(
          align = "left",
          weight = 'bold',
          color = team_color
        )
      ),
      locations = list(
        cells_title(groups = c("title"))
      )
    ) |>
    # add source note
    tab_source_note(
      source_note = md("")
    )
}


team_pitching_table_theme <- function(data, ...) {
  data  %>%
    # Relabel columns
    cols_label(
      team = "",
      avg_rk = "avg",
      whip_rk = "whip",
      babip_rk = "babip",
      k9_rk = "k/9",
      bb9_rk = "bb/9",
      kbb_rk = "k/bb",
      hr9_rk = "hr/9",
      hrfb_rk = "hr/fb",
      gb_rk = "gb%",
      fb_rk = "fb%",
      zone_rk = "zone%",
      fstrike_rk = "f-strike%",
      o_swing_rk = "chase%",
      csw_rk = "csw%",
      soft_rk = "soft%",
      med_rk = "med%",
      hard_rk = "hard%",
      barrel_rk = "barrel%",
      era_rk = "era-",
      fip_rk = "fip-",
      xfip_rk = "xfip-",
      siera_rk = "siera"
    ) %>%
    # Make column labels and spanners all caps
    opt_all_caps() %>%
    # add row striping
    opt_row_striping() %>%
    # change overall table styling for borders and striping
    tab_options(
      column_labels.background.color = "#363231",
      table_body.hlines.color = alpha("gray99", alpha = 0),
      table.border.top.style = "hidden",
      table.border.bottom.style = "hidden",
      table.border.top.width = px(3),
      table.border.top.color = alpha("gray99", alpha = 0),
      table.border.bottom.color = alpha("gray99", alpha = 0),
      table.border.bottom.width = px(3),
      column_labels.border.top.width = px(3),
      column_labels.border.top.color = alpha("gray99", alpha = 0),
      column_labels.border.bottom.width = px(3),
      column_labels.border.bottom.color = alpha("#BEC2CB", alpha = 1),
      heading.title.font.size = 10,
      heading.align = "left",
      
      #row.striping.background_color = "#f9f9fb",
      column_labels.font.size = 8,
      column_labels.font.weight = "bold",
      table.margin.left = px(50),
      ...
    ) %>%
    cols_width(
      fstrike_rk ~ px(52),
      everything() ~ px(48.1)
    ) %>% 
    # change color of border separating the text from the sourcenote
    tab_style(
      style = cell_borders(
        sides = "bottom", color = "#585d63", weight = px(2)
      ),
      locations = cells_body(
        columns = everything(),
        rows = nrow(data$`_data`)
      )
    ) %>%
    #center align values
    tab_style(
    style = cell_text(align = "center"),
    locations = cells_body(
      columns = everything())) %>%
    #center align col headers
    tab_style(
      style = cell_text(align = "center"),
      locations = cells_column_labels(
        columns = everything())) %>%
    #prevent team name from wrapping
    tab_style(
      style = cell_text(whitespace = "nowrap", size = px(12), color = "black", align = "left"),
      locations = cells_body(
        columns = team,
    )) %>%
    # change font to Lato throughout (note no need to have Lato locally!)
    opt_table_font(
      font = c(
        google_font(name = "Exo 2"),
        default_fonts()
      )
    ) %>%
    #change table heading color
      tab_style(
    style = list(
      cell_text(
        align = "left",
        weight = 'bold',
        color = team_color
      )
    ),
    locations = list(
      cells_title(groups = c("title"))
    )
  ) %>%
    # add source note
    tab_source_note(
      source_note = md("")
    )
}


team_pitching_splits_table_theme <- function(data, ...) {
  data  %>%
    # Relabel columns
    cols_label(
      team = "",
      avg_rk = "avg",
      obp_rk = "obp",
      slg_rk = "slg",
      kbb_rk = "k/bb",
      woba_rk = "woba",
      fip_rk = "fip",
      xfip_rk = "xfip",
    ) %>%
    # Make column labels and spanners all caps
    opt_all_caps() %>%
    # add row striping
    opt_row_striping() %>%
    # change overall table styling for borders and striping
    tab_options(
      column_labels.background.color = "#363231",
      table_body.hlines.color = alpha("gray99", alpha = 0),
      table.border.top.style = "hidden",
      table.border.bottom.style = "hidden",
      table.border.top.width = px(3),
      table.border.top.color = alpha("gray99", alpha = 0),
      table.border.bottom.color = alpha("gray99", alpha = 0),
      table.border.bottom.width = px(3),
      column_labels.border.top.width = px(3),
      column_labels.border.top.color = alpha("gray99", alpha = 0),
      column_labels.border.bottom.width = px(3),
      column_labels.border.bottom.color = alpha("#BEC2CB", alpha = 1),
      heading.title.font.size = 10,
      heading.align = "left",
      
      #row.striping.background_color = "#f9f9fb",
      column_labels.font.size = 8,
      column_labels.font.weight = "bold",
      table.margin.left = px(50),
      ...
    ) |>
    cols_width(
      1 ~ px(42),
      2 ~ px(53),
      3 ~ px(53),
      4 ~ px(53),
      5 ~ px(53),
      6 ~ px(53),
      7 ~ px(53),
      8 ~ px(53),
      9 ~ px(53),
      10 ~ px(53),
      11 ~ px(53),
      12 ~ px(53),
      13 ~ px(53),
      14 ~ px(53),
      15 ~ px(53),
      16 ~ px(53)
    ) |>
    # change color of border separating the text from the sourcenote
    tab_style(
      style = cell_borders(
        sides = "bottom", color = "#585d63", weight = px(2)
      ),
      locations = cells_body(
        columns = everything(),
        rows = nrow(data$`_data`)
      )
    ) %>%
    #center align values
    tab_style(
    style = cell_text(align = "center"),
    locations = cells_body(
      columns = everything())) %>%
    #center align col headers
    tab_style(
      style = cell_text(align = "center"),
      locations = cells_column_labels(
        columns = everything())) %>%
    #prevent team name from wrapping
    tab_style(
      style = cell_text(whitespace = "nowrap", size = px(12), color = "black", align = "left"),
      locations = cells_body(
        columns = team,
    )) %>%
    #split type font adjustment
    tab_style(
      style = cell_text(size = px(12), color = "black", align = "center"),
      locations = cells_body(
        columns = split,
      )) %>%
    # change font to Lato throughout (note no need to have Lato locally!)
    opt_table_font(
      font = c(
        google_font(name = "Exo 2"),
        default_fonts()
      )
    ) %>%
     #change table heading color
      tab_style(
    style = list(
      cell_text(
        align = "left",
        weight = 'bold',
        color = team_color
      )
    ),
    locations = list(
      cells_title(groups = c("title"))
    )
  ) %>%
    # add source note
    tab_source_note(
      source_note = md("")
    )
}


player_pitching_splits_table_theme <- function(data, ...) {
  data  %>%
    # Relabel columns
    cols_label(
      name = "",
      avg_rk = "avg",
      obp_rk = "obp",
      slg_rk = "slg",
      kbb_rk = "k/bb",
      woba_rk = "woba",
      fip_rk = "fip",
      xfip_rk = "xfip",
    ) %>%
    # Make column labels and spanners all caps
    opt_all_caps() %>%
    # add row striping
    opt_row_striping() %>%
    # change overall table styling for borders and striping
    tab_options(
      column_labels.background.color = "#363231",
      table_body.hlines.color = alpha("gray99", alpha = 0),
      table.border.top.style = "hidden",
      table.border.bottom.style = "hidden",
      table.border.top.width = px(3),
      table.border.top.color = alpha("gray99", alpha = 0),
      table.border.bottom.color = alpha("gray99", alpha = 0),
      table.border.bottom.width = px(3),
      row_group.font.size = 9,
      row_group.padding = px(1),
      row_group.border.top.color = alpha("gray99", alpha = 0),
      row_group.border.bottom.width = px(.2),
      row_group.border.bottom.color = alpha("#BEC2CB", alpha = .3),
      column_labels.border.top.width = px(3),
      column_labels.border.top.color = alpha("gray99", alpha = 0),
      column_labels.border.bottom.width = px(3),
      column_labels.border.bottom.color = alpha("#BEC2CB", alpha = 1),
      heading.title.font.size = 10,
      heading.align = "left",
      
      #row.striping.background_color = "#f9f9fb",
      column_labels.font.size = 8,
      column_labels.font.weight = "bold",
      table.margin.left = px(50),
      ...
    ) |>
    cols_width(
      1 ~ px(42),
      2 ~ px(53),
      3 ~ px(53),
      4 ~ px(53),
      5 ~ px(53),
      6 ~ px(53),
      7 ~ px(53),
      8 ~ px(53),
      9 ~ px(53),
      10 ~ px(53),
      11 ~ px(53),
      12 ~ px(53),
      13 ~ px(53),
      14 ~ px(53),
      15 ~ px(53),
      16 ~ px(53),
      17 ~ px(53),
      18 ~ px(80)
    ) |>
    #center align values
    tab_style(
    style = cell_text(align = "center"),
    locations = cells_body(
      columns = everything())) %>%
    #center align col headers
    tab_style(
      style = cell_text(align = "center"),
      locations = cells_column_labels(
        columns = everything())) %>%
    #prevent player name from wrapping
    tab_style(
      style = cell_text(whitespace = "nowrap", size = px(12), color = "black", align = "left"),
      locations = cells_body(
        columns = name,
    )) %>%
    #ip
    tab_style(
      style = cell_text(size = px(12), color = "black", align = "center"),
      locations = cells_body(
        columns = c(ip)
      )) %>%
    #split type font adjustment
    tab_style(
      style = cell_text(size = px(12), color = "black", align = "center"),
      locations = cells_body(
        columns = split,
      )) %>%
    # change font to Lato throughout (note no need to have Lato locally!)
    opt_table_font(
      font = c(
        google_font(name = "Exo 2"),
        default_fonts()
      )
    ) %>%
     #change table heading color
      tab_style(
    style = list(
      cell_text(
        align = "left",
        weight = 'bold',
        color = team_color
      )
    ),
    locations = list(
      cells_title(groups = c("title"))
    )
  ) %>%
    # add source note
    tab_source_note(
      source_note = md("")
    )
}



player_pitching_table_theme <- function(data, ...) {
  data  %>%
    # Relabel columns
    cols_label(
      name = "",
      avg_rk = "avg",
      whip_rk = "whip",
      babip_rk = "babip",
      k9_rk = "k/9",
      bb9_rk = "bb9",
      kbb_rk = "k/bb",
      hr9_rk = "hr/9",
      hrfb_rk = "hr/fb",
      gb_rk = "gb%",
      fb_rk = "fb%",
      zone_rk = "zone%",
      fstrike_rk = "f-strike%",
      o_swing_rk = "chase%",
      csw_rk = "csw%",
      soft_rk = "soft%",
      med_rk = "med%",
      hard_rk = "hard%",
      barrel_rk = "barrel%",
      era_rk = "era-",
      fip_rk = "fip-",
      xfip_rk = "xfip-",
      siera_rk = "siera",
      war_rk = "war"
    ) %>%
    # Make column labels and spanners all caps
    opt_all_caps() %>%
    # add row striping
    opt_row_striping() %>%
    # change overall table styling for borders and striping
    tab_options(
      column_labels.background.color = "#363231",
      table_body.hlines.color = alpha("gray99", alpha = 0),
      table.border.top.style = "hidden",
      table.border.bottom.style = "hidden",
      table.border.top.width = px(3),
      table.border.top.color = alpha("gray99", alpha = 0),
      table.border.bottom.color = alpha("gray99", alpha = 0),
      table.border.bottom.width = px(3),
      column_labels.border.top.width = px(3),
      column_labels.border.top.color = alpha("gray99", alpha = 0),
      column_labels.border.bottom.width = px(3),
      column_labels.border.bottom.color = alpha("#BEC2CB", alpha = 1),
      heading.title.font.size = 10,
      heading.align = "left",
      
      #row.striping.background_color = "#f9f9fb",
      column_labels.font.size = 8,
      column_labels.font.weight = "bold",
      table.margin.left = px(50),
      ...
    ) %>%
    cols_width(
      1 ~ px(118),
      ip ~ px(32.2),
      gs ~ px(32.2),
      fstrike_rk ~ px(52),
      barrel_rk ~ px(52),
      everything() ~ px(39.2)
    ) %>% 
    # change color of border separating the text from the sourcenote
    tab_style(
      style = cell_borders(
        sides = "bottom", color = "#585d63", weight = px(2)
      ),
      locations = cells_body(
        columns = everything(),
        rows = nrow(data$`_data`)
      )
    ) %>%
    #center align values
    tab_style(
    style = cell_text(align = "center"),
    locations = cells_body(
      columns = everything())) %>%
    #center align col headers
    tab_style(
      style = cell_text(align = "center"),
      locations = cells_column_labels(
        columns = everything())) %>%
    #prevent player name from wrapping
    tab_style(
      style = cell_text(whitespace = "nowrap", size = px(12), color = "black", align = "left"),
      locations = cells_body(
        columns = name,
    )) %>%
    #ip + gs font adjustment
    tab_style(
      style = cell_text(size = px(12), color = "black", align = "center"),
      locations = cells_body(
        columns = c(ip, gs)
      )) %>%
    # change font to Lato throughout (note no need to have Lato locally!)
    opt_table_font(
      font = c(
        google_font(name = "Exo 2"),
        default_fonts()
      )
    ) %>%
    #change table heading color
      tab_style(
    style = list(
      cell_text(
        align = "left",
        weight = 'bold',
        color = team_color
      )
    ),
    locations = list(
      cells_title(groups = c("title"))
    )
  ) %>%
    # add source note
    tab_source_note(
      source_note = md("")
    )
}

#stack label on top of percentile rank for columns that should be highlighted
stack_function_colors <- function(x){
  
  model <- sub(x = x, pattern = " .*$", replacement = "")
  name <- sub(x = x, pattern = ".*? ", replacement = "")
  
  ifelse(as.numeric(model) >= 75,  
         glue::glue(
           "<div style='line-height:11px'>
<span style='color:black;small-caps;font-size:12px'>
{name}</div>
<div style='line-height:11px'>
<span style ='font-weight:bold;background-color: #169D82;color:white;font-size:8px;padding-left:3px;padding-right:3px;'>
{model}</span></div>"
         ),ifelse(as.numeric(model) <= 25,
                  glue::glue(
                    "<div style='line-height:11px'>
<span style='color:black;small-caps;font-size:12px'>
{name}</div>
<div style='line-height:11px'>
<span style ='font-weight:bold;background-color:#F4D166;color:black;font-size:8px;padding-left:3px;padding-right:3px;'>
{model}</span></div>"
                  ),glue::glue(
                    "<div style='line-height:11px'>
<span style='color:black;small-caps;font-size:12px'>
{name}</div>
<div style='line-height:11px'>
<span style ='color:black;font-size:8px'>
{model}</span></div>")))
}

#stack label on top of league rank for columns that should be highlighted
stack_function_rk_colors <- function(x){
  
  model <- sub(x = x, pattern = " .*$", replacement = "")
  name <- sub(x = x, pattern = ".*? ", replacement = "")
  
  ifelse(as.numeric(model) <= 8,  
         glue::glue(
           "<div style='line-height:11px'>
<span style='color:black;small-caps;font-size:12px'>
{name}</div>
<div style='line-height:11px'>
<span style ='font-weight:bold;background-color: #169D82;color:white;font-size:8px;padding-left:3px;padding-right:3px;'>
{model}</span></div>"
         ),ifelse(as.numeric(model) >= 24,
                  glue::glue(
                    "<div style='line-height:11px'>
<span style='color:black;small-caps;font-size:12px'>
{name}</div>
<div style='line-height:11px'>
<span style ='font-weight:bold;background-color:#F4D166;color:black;font-size:8px;padding-left:3px;padding-right:3px;'>
{model}</span></div>"
                  ),glue::glue(
                    "<div style='line-height:11px'>
<span style='color:black;small-caps;font-size:12px'>
{name}</div>
<div style='line-height:11px'>
<span style ='color:black;font-size:8px'>
{model}</span></div>")))
}


#stack label on top of percentile rank for columns that should not be highlighted
stack_function_black <- function(x){
  
  model <- sub(x = x, pattern = " .*$", replacement = "")
  name <- sub(x = x, pattern = ".*? ", replacement = "")
  
  
glue::glue("<div style='line-height:11px'>
<span style='color:black;small-caps;font-size:12px'>
{name}</div>
<div style='line-height:11px'>
<span style ='color:black;font-size:8px;padding-left:3px;padding-right:3px;'>
{model}</span></div>")
}





#radar plot
library(fmsb)
radar_plot_data <- read.csv("radar_plot_data.csv")

radar_plot_func <- function(data, color = c("#b6e3d7", "#137a63"), 
                                        vlabels = colnames(data), vlcex = 0.7,
                                        caxislabels = NULL, title = NULL, ...){
  radarchart(
    data, axistype = 1,
    # Customize the polygon
    pcol = color, pfcol = alpha(color, 0.3), plwd = 4, plty = 1,
    # Customize the grid
    cglcol = "grey", cglty = 1, cglwd = 0.5,
    # Customize the axis
    axislabcol = "grey", 
    # Variable labels
    vlcex = vlcex, vlabels = vlabels,
    caxislabels = caxislabels, title = title, ...
  )
}

```


```{r render subpages, include=FALSE}
# Get all unique product groups for the subpages
teams <- as.character(mlb_standings_max$team_abbr)
#only do one team
teams <- "CHC"

# Create variable which, stores all subpages outputs
out = NULL

# Set knitr options to allow duplicate labels (needed for the subpages)
options(knitr.duplicate.label = 'allow')

# Create temporary environment which we use for knitting subpages.RMD 

team_env <- new.env()


for (t in teams) {
  # Filter player_batting
  player_batting_team <- player_batting %>% 
    filter(team == t)
  
  # Filter team_batting
  team_batting_team <- team_batting %>% 
    filter(team == t)
  
  # Filter team_batting_splits
  team_batting_splits_team <- team_batting_splits %>% 
    filter(team == t)
  
  player_batting_splits_team <- player_batting_splits %>% 
    filter(team == t)
  
   # Filter team_pitching
  team_pitching_team <- team_pitching %>% 
    filter(team == t)
  
  # Filter team_pitching splits
  team_pitching_splits_team <- team_pitching_splits %>% 
    filter(team == t)
  
   # Filter player_starting_pitching
  player_starting_pitching_team <- player_starting_pitching %>% 
    filter(team == t)
  
    # Filter player_starting_pitching
  player_relief_pitching_team <- player_relief_pitching %>% 
    filter(team == t)
  
  player_pitching_splits_team <- player_pitching_splits %>% 
    filter(team == t)
  
  #filter radar plot
  radar_plot_data_team <- radar_plot_data %>% 
    filter(team == t)
  
  # create variables to use for each team in loop
  logo <- toString(mlb_standings_max %>% filter(team_abbr == t) %>% select(team_logo_espn))
  logo2 <- toString(mlb_standings_max %>% filter(team_abbr == t) %>% select(team_scoreboard_logo_espn))
  logo3 <- toString(mlb_standings_max %>% filter(team_abbr == t) %>% select(team_cap_logo_on_light))
  logo4 <- toString(mlb_standings_max %>% filter(team_abbr == t) %>% select(team_cap_logo_on_dark))
  team_color <- toString(mlb_standings_max %>% filter(team_abbr == t) %>% select(team_color))
  team_color2 <- toString(mlb_standings_max %>% filter(team_abbr == t) %>% select(team_color2))
  gg_color <- toString(mlb_standings_max %>% filter(team_abbr == t) %>% select(gg_color))
  gg_fill_color <- toString(mlb_standings_max %>% filter(team_abbr == t) %>% select(gg_fill_color))
  team <- toString(mlb_standings_max %>% filter(team_abbr == t) %>% select(team))
  division <- toString(mlb_standings_max %>% filter(team_abbr == t) %>% select(division_name))
  
  # Assign filtered player_batting and product group to subpage_env 
  assign("player_batting_team", player_batting_team, team_env)

  


  
  # Knit subpage.RMD using the subpage_env and add result to out vector
  out = c(out, knitr::knit_child('subpage.RMD', envir = team_env))
}
```

`r paste(knitr::knit_child(text = out), collapse = '')`

::: {.doc_main}
\newpage
<br>
<br>
**About the Data**

- Player batting tables are filtered and sorted based on top 10 players in plate appearances
- Player pitching tables are filtered and sorted based on top 7 players in total batters faced
- Player batting splits tables are filtered and sorted based on top 10 players in plate appearances
  - only players who have faced both LHP and RHP are displayed
- Player pitching splits tables are filtered and sorted based on top 10 players in total batters faced
  - only players who have faced both LHH and RHH are displayed
- In each table, the top values are the actual values for the statistic
  - For the team tables, the bottom values are the league rank (1 is best; 30 is worst)
    - Top 8 in the league values are highlighted <span style="padding-top: 0px;  padding-bottom: 4px; padding-left: 2px; padding-right: 2px; color:white !important; background-color:#169D82 !important">green</span>
    - Bottom 8 in the league values are highlighted <span style="padding-top: 0px; padding-bottom: 4px; padding-left: 2px; padding-right: 2px; background-color:#F4D166 !important">gold</span>
  - For the player tables, the bottom values are the percentile rank (100 is best; 0 is worst)
    - Top 25 percentile values are highlighted <span style="padding-top: 0px; padding-bottom: 4px; padding-left: 2px; padding-right: 2px; color:white !important; background-color:#169D82 !important">green</span>
    - Bottom 25 percentile values are highlighted <span style="padding-top: 0px; padding-bottom: 4px; padding-left: 2px; padding-right: 2px; background-color:#F4D166 !important">gold</span>
      

**Glossary**

<div style="float: left; width: 390px; line-height: 1;">
**PA** Plate Appearances

**IP** Innings Pitched

**GS** Games Started

**AVG** Batting Average

**OBP** On Base Percentage

**SLG** Slugging Percentage

**ISO** Isolated Power – (SLG - AVG)

**BB%** Walk %

**K%** Strikeout %

**BB/K** Walk to Strikeout Ratio

**K/BB** Strikeout to Walk Ratio

**BABIP** Batting Average of Balls in Play

**K/9** Strikeouts / 9 Innings

**BB/9** Walks / 9 Innings

**SOFT%** Soft Hit Balls / Batted Balls

**MED%** Medium Hit Balls / Batted Balls

**HARD%** Hard Hit Balls / Batted Balls

**BARREL%** Hard Hit Balls leading to >= .500 AVG & 1.500 SLG

**PULL%** Pulled Batted Balls / Batted Balls

**CENTER%** Center of Field Batted Balls / Batted Balls
</div>
<div style="float: right; width: 390px; line-height: 1;">
**OPPO%** Opposite Field Batted Balls / Batted Balls

**WRC+** Runs Created Adjusted for Run Environment

**WHIP** Walked + Hits / IP

**GB%** Ground Balls / Balls in Play

**FB%** Fly Balls / Balls in Play

**HR/FB** Home runs / Fly Balls

**HR/9** Home runs / 9 innings

**ZONE%** Percentage of Pitches in Strike Zone

**F-STRIKE%** First Pitch Strike Percentage

**CHASE%** Swings at Pitches Outside Zone / Pitches Outside Zone

**CSW%** Called Strikes + Swings and Misses / Total Pitches

**CONTACT%** Contact Swings / Totals Swings

**ERA-** Adjusted Earned Run Average

**FIP-** Adjusted Fielder Independent Pitching

**XFIP-** Adjusted Expected FIP

**SIERA** Skill Interactive Earned Run Average

**WAR** Wins Above Replacement

**XBA** Expected Batting Average

**XSLG** Expected Slugging Percentage

**XWOBA** Expected Weighted On Base Average
</div>
:::



